---
title: "Main_data_Models"
output: html_document
date: "2023-12-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Version-1 Model

in.sqft
in.bedrooms
in.building_america_climate_zone
in.ceiling_fan
in.cooling_setpoint
in.cooling_setpoint_has_offset
in.cooling_setpoint_offset_magnitude
in.cooling_setpoint_offset_period
in.ducts
in.geometry_foundation_type
in.geometry_wall_type
in.has_pv
in.heating_fuel
in.hot_water_fixtures
in.hvac_cooling_partial_space_conditioning
in.hvac_cooling_type
in.hvac_heating_type
in.hvac_heating_type_and_fuel
in.insulation_ceiling
in.insulation_wall
in.lighting
in.misc_extra_refrigerator
in.misc_freezer
in.misc_pool_pump
in.occupants
in.pv_system_size
in.refrigerator
in.roof_material
in.usage_level
in.vacancy_status
in.water_heater_efficiency
in.water_heater_fuel

```{r}

library (arrow)
library(arrow)
library(tidyverse)
Merged_Final<-read_parquet("Aggregate_Final_Dataset.parquet")
```

```{r}
str(Merged_Final)


```

```{r}
# cols_1<-c('in.sqft',
# 'in.bedrooms',
# 'in.building_america_climate_zone',
# 'in.ceiling_fan',
# 'in.cooling_setpoint',
# 'in.cooling_setpoint_has_offset',
# 'in.cooling_setpoint_offset_magnitude',
# 'in.cooling_setpoint_offset_period',
# 'in.ducts',
# 'in.geometry_foundation_type',
# 'in.geometry_wall_type',
# 'in.has_pv',
# 'in.heating_fuel',
# 'in.hot_water_fixtures',
# 'in.hvac_cooling_partial_space_conditioning',
# 'in.hvac_cooling_type',
# 'in.hvac_heating_type',
# 'in.hvac_heating_type_and_fuel',
# 'in.insulation_ceiling',
# 'in.insulation_wall',
# 'in.lighting',
# 'in.misc_extra_refrigerator',
# 'in.misc_freezer',
# 'in.misc_pool_pump',
# 'in.occupants',
# 'in.pv_system_size',
# 'in.refrigerator',
# 'in.roof_material',
# 'in.usage_level',
# 'in.vacancy_status',
# 'in.water_heater_efficiency',
# 'in.water_heater_fuel',
# 'Final_Energy_KWH'
# )
# 
# Subset_V1<-Merged_Final[,cols_1]
```



```{r}
# str(Subset_V1)
# non_numeric_cols <- sapply(Subset_V1, function(x) !is.numeric(x))
# Subset_V1[non_numeric_cols] <- lapply(Subset_V1[non_numeric_cols], as.factor)
# str(Subset_V1)
# 
# 
# 
# # Example assuming 'energy_consumption' is the target variable
# model_lm <- lm( Final_Energy_KWH~ ., data = Subset_V1)
# summary(model_lm)

```



```{r}
cols_2<-c(
'Dry Bulb Temperature [°C]',
'Relative Humidity [%]',
'Global Horizontal Radiation [W/m2]',
'in.sqft',
'in.bedrooms',
'in.building_america_climate_zone',
'in.ceiling_fan',
'in.cooling_setpoint',
'in.cooling_setpoint_has_offset',
'in.cooling_setpoint_offset_magnitude',
'in.clothes_dryer',
'in.clothes_washer',
'in.ducts',
'in.geometry_foundation_type',
'in.geometry_wall_type',
'in.has_pv',
'in.heating_fuel',
'in.hot_water_fixtures',
'in.hvac_cooling_partial_space_conditioning',
'in.hvac_cooling_type',
'in.hvac_heating_type',
'in.insulation_ceiling',
'in.insulation_wall',
'in.lighting',
'in.misc_extra_refrigerator',
'in.misc_freezer',
'in.misc_pool_pump',
'in.occupants',
'in.pv_system_size',
'in.refrigerator',
'in.roof_material',
'in.usage_level',
'in.vacancy_status',
'in.water_heater_efficiency',
'in.water_heater_fuel',
'Final_Energy_KWH'
)

Subset_V2<-Merged_Final[,cols_2]
```



```{r}
str(Subset_V2)
non_numeric_cols <- sapply(Subset_V2, function(x) !is.numeric(x))
Subset_V2[non_numeric_cols] <- lapply(Subset_V2[non_numeric_cols], as.factor)
str(Subset_V2)



# Example assuming 'energy_consumption' is the target variable
model_lm_2 <- lm( Final_Energy_KWH~ ., data = Subset_V2)
summary(model_lm_2)

```
#Model 3

```{r}
cols_3<-c(
  'Dry Bulb Temperature [°C]',
   'Relative Humidity [%]',
  'in.county',
  'hour',
  'Global Horizontal Radiation [W/m2]',
  'in.sqft',
'in.bedrooms',
'in.building_america_climate_zone',
'in.ceiling_fan',
'in.cooling_setpoint',
'in.cooling_setpoint_has_offset',
'in.cooling_setpoint_offset_magnitude',
#-----------
'in.clothes_dryer',
'in.clothes_washer',
'in.insulation_slab',
'Wind Speed [m/s]',
#-------------------
'in.ducts',
'in.geometry_foundation_type',
'in.geometry_wall_type',
'in.has_pv',
'in.heating_fuel',
'in.hot_water_fixtures',
'in.hvac_cooling_partial_space_conditioning',
'in.hvac_cooling_type',
'in.hvac_heating_type',
#'in.hvac_heating_type_and_fuel',
'in.insulation_ceiling',
'in.insulation_wall',
'in.lighting',
'in.misc_extra_refrigerator',
'in.misc_freezer',
'in.misc_pool_pump',
'in.occupants',
'in.pv_system_size',
'in.refrigerator',
'in.roof_material',
'in.usage_level',
'in.vacancy_status',
'in.water_heater_efficiency',
'in.water_heater_fuel',
'Final_Energy_KWH'
)

Subset_V3<-Merged_Final[,cols_3]
```



```{r}
str(Subset_V3)
non_numeric_cols <- sapply(Subset_V3, function(x) !is.numeric(x))
Subset_V3[non_numeric_cols] <- lapply(Subset_V3[non_numeric_cols], as.factor)
str(Subset_V3)



# Example assuming 'energy_consumption' is the target variable
model_lm_3 <- lm( Final_Energy_KWH~ ., data = Subset_V3)
summary(model_lm_3)

```
Final Model
```{r}
library(arrow)
library(tidyverse)



cols_4<-c('hour',
          'in.county',
          'Dry Bulb Temperature [°C]','Relative Humidity [%]','Wind Speed [m/s]',
          'Wind Direction [Deg]','Direct Normal Radiation [W/m2]','Diffuse Horizontal Radiation [W/m2]',
          'Global Horizontal Radiation [W/m2]', 'in.sqft',
          'in.bedrooms',
          'in.building_america_climate_zone',
          'in.ceiling_fan',
          'in.clothes_dryer',
          'in.clothes_washer',
          'in.cooling_setpoint',
          'in.cooling_setpoint_has_offset',
          'in.cooling_setpoint_offset_magnitude',
          'in.dishwasher',
          'in.ducts',
          'in.geometry_foundation_type',
          'in.geometry_wall_type',
          'in.geometry_stories',
          'in.has_pv',
          'in.heating_fuel',
          'in.hot_water_fixtures',
          'in.hvac_cooling_partial_space_conditioning',
          'in.hvac_cooling_type',
          'in.hvac_heating_type',
          'in.hvac_heating_type_and_fuel',
          'in.infiltration',
          'in.insulation_ceiling',
          'in.insulation_wall',
          'in.lighting',
          'in.misc_extra_refrigerator',
          'in.misc_freezer',
          'in.misc_pool_pump',
          'in.occupants',
          'in.pv_system_size',
          'in.refrigerator',
          'in.roof_material',
          'in.usage_level',
          'in.vacancy_status',
          'in.water_heater_efficiency',
          'in.water_heater_fuel',
          'Final_Energy_KWH'
          
)

Subset_V4<-Merged_Final[,cols_4]

non_numeric_cols <- sapply(Subset_V4, function(x) !is.numeric(x))
Subset_V4[non_numeric_cols] <- lapply(Subset_V4[non_numeric_cols], as.factor)

#xGBoost Model
set.seed(123)

# Split data into training and test sets (e.g., 80% training, 20% test)
train_indices <- sample(1:nrow(Subset_V4), size = 0.7 * nrow(Subset_V4))
train_data <- Subset_V4[train_indices, ]
test_data <- Subset_V4[-train_indices, ]


library (xgboost)

# Convert training data to DMatrix format
dtrain <- xgb.DMatrix(data = data.matrix(train_data[, -which(names(train_data) == "Final_Energy_KWH")]), 
                      label = train_data$Final_Energy_KWH)

params <- list(
  objective = "reg:squarederror",
  eta = 0.1,
  max_depth = 8,
  subsample = 0.5,
  colsample_bytree = 0.5
)

nrounds <- 3000  # Number of boosting rounds. Adjust based on your dataset and needs

xgb_model <- xgboost(params = params, data = dtrain, nrounds = nrounds)

#summary(xgb_model)


# Assuming you have a trained XGBoost model 'xgb_model' and a test set 'test_data'

# Predict on the test set
dtest <- xgb.DMatrix(data = data.matrix(test_data[, -which(names(test_data) == "Final_Energy_KWH")]))
predictions1 <- predict(xgb_model, dtest)

# Compute RMSE
rmse <- sqrt(mean((predictions1 - test_data$Final_Energy_KWH)^2))
#print(paste("RMSE:", rmse))

# Compute R-squared
SST <- sum((test_data$Final_Energy_KWH - mean(test_data$Final_Energy_KWH))^2)
SSR <- sum((predictions1 - test_data$Final_Energy_KWH)^2)
r_squared <- 1 - SSR/SST
print(paste("R-squared:", r_squared))


#range(predictions1-test_data$Final_Energy_KWH)
#summary(predictions1-test_data$Final_Energy_KWH) 
# Visualize feature importance
```


```{r}
importance_matrix <- xgb.importance(model = xgb_model)
print(importance_matrix)
# Visualize feature importance
xgb.plot.importance(importance_matrix)


```

```{r}

Test_Optimied_Variables <-Subset_V4
#Test_Optimied_Variables$in.insulation_wall<-"Brick, 12-in, 3-wythe, R-7"
#Test_Optimied_Variables$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
#Test_Optimied_Variables$in.usage_level<-"Low"
Test_Optimied_Variables$`Dry Bulb Temperature [°C]`<-Test_Optimied_Variables$`Dry Bulb Temperature [°C]`+5

dtest2 <- xgb.DMatrix(data = data.matrix(Test_Optimied_Variables[, -which(names(test_data) == "Final_Energy_KWH")]))

predictions1 <- predict(xgb_model, dtest2)
#actual vs predicted reduced due to upgrades
df_new = data.frame(predictions1,Subset_V4$Final_Energy_KWH)
#df_new
#sum(predictions1)
#sum(Subset_V4$Final_Energy_KWH)


data <- data.frame(
  Category = rep(c("Predicted Energy", "Current Energy"),each=nrow(predictions1)),
  Energy_Value = c(predictions1, test_data$Final_Energy_KWH)
)

Test_Optimied_Variables$predictions1<-predictions1

#glimpse(Test_Optimied_Variables)
```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(maps)
#install.packages("mapdata")
library(mapdata)
 ICPSRNAM = c("ABBEVILLE", "AIKEN", "ALLENDALE", "ANDERSON", "BAMBERG", "BARNWELL", "BEAUFORT", "BERKELEY", "CALHOUN", "CHARLESTON", 
               "CHEROKEE", "CHESTER", "CHESTERFIELD", "CLARENDON", "COLLETON", "DARLINGTON", "DILLON", "DORCHESTER", "EDGEFIELD", 
               "FAIRFIELD", "FLORENCE", "GEORGETOWN", "GREENVILLE", "GREENWOOD", "HAMPTON", "HORRY", "JASPER", "KERSHAW", "LANCASTER", 
               "LAURENS", "LEE", "LEXINGTON", "MARION", "MARLBORO", "MCCORMICK", "NEWBERRY", "OCONEE", "ORANGEBURG", "PICKENS", 
               "RICHLAND", "SALUDA", "SPARTANBURG", "SUMTER", "UNION", "WILLIAMSBURG", "YORK")
 
  GISJOIN = c("G4500010", "G4500030", "G4500050", "G4500070", "G4500090", "G4500110", "G4500130", "G4500150", "G4500170", "G4500190", 
              "G4500210", "G4500230", "G4500250", "G4500270", "G4500290", "G4500310", "G4500330", "G4500350", "G4500370", "G4500390", 
              "G4500410", "G4500430", "G4500450", "G4500470", "G4500490", "G4500510", "G4500530", "G4500550", "G4500570", "G4500590", 
              "G4500610", "G4500630", "G4500670", "G4500690", "G4500650", "G4500710", "G4500730", "G4500750", "G4500770", "G4500790", 
              "G4500810", "G4500830", "G4500850", "G4500870", "G4500890", "G4500910")
# Calculate total energy by county
List_Name<-data.frame(tolower(ICPSRNAM),(GISJOIN))
#List_Name
energy_data <- Subset_V4 %>%
  group_by(in.county) %>%
  summarize(total_energy = sum(Final_Energy_KWH, na.rm = TRUE))
energy_data$County_name<-List_Name$tolower.ICPSRNAM.[match(energy_data$in.county,List_Name$X.GISJOIN.)]


county_map <- map_data("county", region = "south carolina")
county_map$subregion<-tolower(county_map$subregion)
energy_data$in.county<-tolower(energy_data$in.county)

# Merge energy data with the county map
merged_data <- merge(county_map, energy_data, by.x = "subregion", by.y = "County_name", all.x = TRUE)
#merged_data
# Create the heatmap
ggplot(merged_data, aes(x = long, y = lat, group = group, fill = total_energy)) +
  geom_polygon() +
  scale_fill_gradient(low = "yellow", high = "red") +
  labs(title = "Energy Consumption Heatmap by County in South Carolina") +
  theme_minimal()




```



```{r}


Summarize_Predictions<-Test_Optimied_Variables %>%group_by(in.county) %>%
  summarize(total_energy = sum(Final_Energy_KWH, na.rm = TRUE),predicted_energy=sum(predictions1,na.rm=TRUE))
#str(Summarize_Predictions)
# 
# 
# library(ggplot2)
# 
# # Create a bar plot
# ggplot(data = Summarize_Predictions, aes(x = in.county)) +
#   geom_bar(aes(y = total_energy), stat = "identity", fill = "blue", alpha = 0.6) +
#   geom_bar(aes(y = predicted_energy), stat = "identity", fill = "red", alpha = 0.6) +
#   labs(title = "Total Energy in July vs Predicted Energy (with increase by 5 C) by County",
#        x = "County", y = "Energy") +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
# 


# Calculate percentage difference
Summarize_Predictions$percentage_diff <- ( (Summarize_Predictions$predicted_energy -Summarize_Predictions$total_energy)/Summarize_Predictions$total_energy) * 100

# Create a bar plot with percentage difference labels
ggplot(data = Summarize_Predictions, aes(x = in.county)) +
  geom_bar(aes(y = total_energy), stat = "identity", fill = "blue", alpha = 0.6) +
  geom_bar(aes(y = predicted_energy), stat = "identity", fill = "red", alpha = 0.6) +
  geom_text(aes(y = pmax(predicted_energy, total_energy), 
                label = paste0(round(percentage_diff, 2), "%")), 
            position = position_stack(vjust = 0.5), 
            size = 3, 
            color = "black", 
            angle = 90, 
            hjust = -0.5) +  
  labs(title = "Total Energy in July vs Predicted Energy (with increase by 5 C) by County",
       x = "County", y = "Energy") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))




```

```{r}
sum_energy<-sum(Summarize_Predictions$total_energy)
Predicted<-sum(Summarize_Predictions$predicted_energy)
values <- c(sum_energy, Predicted)

options(scipen = 999) 
# Creating a bar plot
barplot(values, names.arg = c("Total Energy for July", "Predicted Energy with 5 Celcius increase"), col = "lightgreen",
        xlab = "Energy", ylab = "Total Value", main = "Comparison of Total and Predicted Energy")


```

```{r}

Predictions_hour<-Test_Optimied_Variables %>%group_by(hour) %>%
  summarize(total_energy = sum(Final_Energy_KWH, na.rm = TRUE),predicted_energy=sum(predictions1,na.rm=TRUE))

# Calculate percentage difference
Predictions_hour$percentage_diff <- ((Predictions_hour$predicted_energy - Predictions_hour$total_energy) / Predictions_hour$total_energy) * 100

#since temp increse people keep appliances on often
ggplot(data = Predictions_hour, aes(x = hour)) +
  geom_bar(aes(y = total_energy), stat = "identity", fill = "blue", alpha = 0.6) +
  geom_bar(aes(y = predicted_energy), stat = "identity", fill = "red", alpha = 0.6) +
  geom_text(aes(y = pmax(predicted_energy, total_energy), 
                label = paste0(round(percentage_diff, 2), "%")), 
            position = position_stack(vjust = 0.5), 
            size = 3, 
            color = "black", 
            angle = 90, 
            hjust = -0.5) +  
  labs(title = "Total Energy in July vs Predicted Energy (with increase by 5 C) by Hour",
       x = "Hourly", y = "Energy") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

```{r}
Test_Optimied_Variables_reduce <-Subset_V4
Test_Optimied_Variables_reduce$`Dry Bulb Temperature [°C]`<-Test_Optimied_Variables$`Dry Bulb Temperature [°C]`+5
#Test_Optimied_Variables_reduce$in.ceiling_fan<-"Standard Efficiency, No usage"
#Test_Optimied_Variables$in.insulation_wall<-"Brick, 12-in, 3-wythe, R-7"
#Test_Optimied_Variables$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
# Test_Optimied_Variables$in.usage_level<-"Low"
#Test_Optimied_Variables_reduce$in.pv_system_size<-"1.0 kWDC"

# Assuming 'Test_Optimized_Variables_reduce' is your dataset

# Replace "none" with "1kw" in the 'in.pv_system_size' column
#Test_Optimied_Variables_reduce$in.pv_system_size <- ifelse(Test_Optimied_Variables_reduce$in.pv_system_size == "None" , "1.0 kWDC",Test_Optimied_Variables_reduce$in.pv_system_size)

#unique(Test_Optimied_Variables_reduce$in.hvac_cooling_type)
#Test_Optimied_Variables_reduce$in.hvac_cooling_type<-"Central AC"
#Test_Optimied_Variables_reduce$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
#Test_Optimied_Variables_reduce$in.ducts<-"None"
#Test_Optimied_Variables_reduce$in.hot_water_fixtures<-"50% Usage"
dtest2 <- xgb.DMatrix(data = data.matrix(Test_Optimied_Variables_reduce[, -which(names(test_data) == "Final_Energy_KWH")]))

predictions1 <- predict(xgb_model, dtest2)
#actual vs predicted reduced due to upgrades
df_new = data.frame(predictions1,Subset_V4$Final_Energy_KWH)
#df_new
sum(predictions1)
sum(Subset_V4$Final_Energy_KWH)

Test_Optimied_Variables$predictions1<-predictions1
# Calculate the sum of predictions1 and Subset_V4$Final_Energy_KWH
sum_predictions <- sum(predictions1)
sum_final_energy <- sum(Subset_V4$Final_Energy_KWH)

# Calculate the percentage increase
percent_increase <- ((sum_final_energy - sum_predictions) / sum_predictions) * 100

# Create a data frame for plotting
data <- data.frame(
  Variable = c("predictions1", "Subset_V4$Final_Energy_KWH"),
  Sum = c(sum_predictions, sum_final_energy)
)

# Load necessary libraries
library(ggplot2)

# Create a line plot
ggplot(data, aes(x = Variable, y = Sum, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = paste(round(Sum, 2), "")), vjust = -0.5, size = 4) +
  labs(title = "Percentage Increase when temperatures are 5 degree Celcius warmer",
       x = "Temperature increase",
       y = "Sum of Energy") +
  theme_minimal()


```


```{r}
Test_Optimied_Variables_reduce <-Subset_V4
Test_Optimied_Variables_reduce$`Dry Bulb Temperature [°C]`<-Test_Optimied_Variables$`Dry Bulb Temperature [°C]`+5
Test_Optimied_Variables_reduce$in.ceiling_fan<-"Standard Efficiency, No usage"
#Test_Optimied_Variables$in.insulation_wall<-"Brick, 12-in, 3-wythe, R-7"
#Test_Optimied_Variables$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
# Test_Optimied_Variables$in.usage_level<-"Low"
#Test_Optimied_Variables_reduce$in.cooling_setpoint<-"80F"
#Test_Optimied_Variables_reduce$in.pv_system_size<-"1.0 kWDC"

# Assuming 'Test_Optimized_Variables_reduce' is your dataset

# Replace "none" with "1kw" in the 'in.pv_system_size' column
#Test_Optimied_Variables_reduce$in.pv_system_size <- ifelse(Test_Optimied_Variables_reduce$in.pv_system_size == "None" , "1.0 kWDC",Test_Optimied_Variables_reduce$in.pv_system_size)

#unique(Test_Optimied_Variables_reduce$in.hvac_cooling_type)
#Test_Optimied_Variables_reduce$in.hvac_cooling_type<-"Central AC"
#Test_Optimied_Variables_reduce$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
#Test_Optimied_Variables_reduce$in.ducts<-"None"
Test_Optimied_Variables_reduce$in.hot_water_fixtures<-"50% Usage"
dtest2 <- xgb.DMatrix(data = data.matrix(Test_Optimied_Variables_reduce[, -which(names(test_data) == "Final_Energy_KWH")]))

predictions1 <- predict(xgb_model, dtest2)
#actual vs predicted reduced due to upgrades
df_new = data.frame(predictions1,Subset_V4$Final_Energy_KWH)
#df_new
#sum(predictions1)
#sum(Subset_V4$Final_Energy_KWH)

Test_Optimied_Variables$predictions1<-predictions1
# Calculate the sum of predictions1 and Subset_V4$Final_Energy_KWH
sum_predictions <- sum(predictions1)
Final_temp_increase <-sum_predictions 
sum_final_energy <- sum(Subset_V4$Final_Energy_KWH)

# Calculate the percentage increase
percent_increase <- ((sum_final_energy - sum_predictions) / sum_predictions) * 100

# Create a data frame for plotting
data <- data.frame(
  Variable = c("predictions1", "Subset_V4$Final_Energy_KWH"),
  Sum = c(sum_predictions, sum_final_energy)
)

# Load necessary libraries
library(ggplot2)

# Create a line plot
ggplot(data, aes(x = Variable, y = Sum, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = paste(round(Sum, 2), "")), vjust = -0.5, size = 4) +
  labs(title = "Percentage Increase when temperatures are 5 degree Celcius warmer",
       x = "Temperature increase",
       y = "Sum of Energy") +
  theme_minimal()

```


```{r}
Test_Optimied_Variables_reduce <-Subset_V4
Test_Optimied_Variables_reduce$`Dry Bulb Temperature [°C]`<-Test_Optimied_Variables$`Dry Bulb Temperature [°C]`+5
Test_Optimied_Variables_reduce$in.ceiling_fan<-"Standard Efficiency, No usage"
#Test_Optimied_Variables$in.insulation_wall<-"Brick, 12-in, 3-wythe, R-7"
#Test_Optimied_Variables$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
# Test_Optimied_Variables$in.usage_level<-"Low"
#Test_Optimied_Variables_reduce$in.cooling_setpoint<-"80F"
#Test_Optimied_Variables_reduce$in.pv_system_size<-"1.0 kWDC"

# Assuming 'Test_Optimized_Variables_reduce' is your dataset

# Replace "none" with "1kw" in the 'in.pv_system_size' column
#Test_Optimied_Variables_reduce$in.pv_system_size <- ifelse(Test_Optimied_Variables_reduce$in.pv_system_size == "None" , "1.0 kWDC",Test_Optimied_Variables_reduce$in.pv_system_size)

#unique(Test_Optimied_Variables_reduce$in.hvac_cooling_type)
#Test_Optimied_Variables_reduce$in.hvac_cooling_type<-"Central AC"
#Test_Optimied_Variables_reduce$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
#Test_Optimied_Variables_reduce$in.ducts<-"None"
Test_Optimied_Variables_reduce$in.infiltration<-"ACH50 15"

Test_Optimied_Variables_reduce$in.hot_water_fixtures<-"50% Usage"
dtest2 <- xgb.DMatrix(data = data.matrix(Test_Optimied_Variables_reduce[, -which(names(test_data) == "Final_Energy_KWH")]))

predictions1 <- predict(xgb_model, dtest2)
#actual vs predicted reduced due to upgrades
df_new = data.frame(predictions1,Final_temp_increase )
#df_new
#sum(predictions1)
#sum(Subset_V4$Final_Energy_KWH)

Test_Optimied_Variables$predictions1<-predictions1
# Calculate the sum of predictions1 and Subset_V4$Final_Energy_KWH
sum_predictions <- sum(predictions1)
sum_final_energy <- Final_temp_increase 

# Calculate the percentage increase
percent_increase <- ((sum_final_energy - sum_predictions) / sum_predictions) * 100

# Create a data frame for plotting
data <- data.frame(
  Variable = c("predictions with optimization", "5 Degree Predicted Energy Consumption "),
  Sum = c(sum_predictions, sum_final_energy)
)

# Load necessary libraries
library(ggplot2)

# Create a line plot
ggplot(data, aes(x = Variable, y = Sum, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = paste(round(Sum, 2), "")), vjust = -0.5, size = 4) +
  labs(title = "Percentage Decrease with Optimization",
       x = "Temeprature Increase - optimizing fan usage and hot water fixtures",
       y = "Sum of Energy") +
  theme_minimal()

```

```{r}
Test_Optimied_Variables_reduce <-Subset_V4
Test_Optimied_Variables_reduce$`Dry Bulb Temperature [°C]`<-Test_Optimied_Variables$`Dry Bulb Temperature [°C]`+5
#Test_Optimied_Variables_reduce$in.ceiling_fan<-"Standard Efficiency, No usage"
#Test_Optimied_Variables$in.insulation_wall<-"Brick, 12-in, 3-wythe, R-7"
#Test_Optimied_Variables$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
# Test_Optimied_Variables$in.usage_level<-"Low"
#Test_Optimied_Variables_reduce$in.cooling_setpoint<-"80F"
#Test_Optimied_Variables_reduce$in.pv_system_size<-"1.0 kWDC"

# Assuming 'Test_Optimized_Variables_reduce' is your dataset

# Replace "none" with "1kw" in the 'in.pv_system_size' column
Test_Optimied_Variables_reduce$in.pv_system_size <- ifelse(Test_Optimied_Variables_reduce$in.pv_system_size == "None" , "1.0 kWDC",Test_Optimied_Variables_reduce$in.pv_system_size)

#unique(Test_Optimied_Variables_reduce$in.hvac_cooling_type)
#Test_Optimied_Variables_reduce$in.hvac_cooling_type<-"Central AC"
#Test_Optimied_Variables_reduce$in.hvac_cooling_partial_space_conditioning<-"40% Conditioned"
#Test_Optimied_Variables_reduce$in.ducts<-"None"
#Test_Optimied_Variables_reduce$in.infiltration<-"ACH50 15"

#Test_Optimied_Variables_reduce$in.hot_water_fixtures<-"50% Usage"
dtest2 <- xgb.DMatrix(data = data.matrix(Test_Optimied_Variables_reduce[, -which(names(test_data) == "Final_Energy_KWH")]))

predictions1 <- predict(xgb_model, dtest2)
#actual vs predicted reduced due to upgrades
df_new = data.frame(predictions1,Final_temp_increase )
#df_new
#sum(predictions1)
#sum(Subset_V4$Final_Energy_KWH)

Test_Optimied_Variables$predictions1<-predictions1
# Calculate the sum of predictions1 and Subset_V4$Final_Energy_KWH
sum_predictions <- sum(predictions1)
sum_final_energy <- Final_temp_increase 

# Calculate the percentage increase
percent_increase <- ((sum_final_energy - sum_predictions) / sum_predictions) * 100

# Create a data frame for plotting
data <- data.frame(
  Variable = c("predictions with optimization", "5 Degree Predicted Energy Consumption "),
  Sum = c(sum_predictions, sum_final_energy)
)

# Load necessary libraries
library(ggplot2)

# Create a line plot
ggplot(data, aes(x = Variable, y = Sum, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "blue", size = 3) +
  geom_text(aes(label = paste(round(Sum, 2), "")), vjust = -0.5, size = 4) +
  labs(title = "Percentage Decrease with Optimization",
       x = "Temeprature Increase - optimizing PV usage",
       y = "Sum of Energy") +
  theme_minimal()

```